### 2018-07-06 paper/1-intro.tex
Link to build-1.0 on Hackage

\item We show that we can instantiate our abstractions to describe the essence
of a variety of different real-life build systems, including \Make, \Shake,
\Bazel, \CloudBuild, \Buck, \Nix, and \Excel\footnote{\Excel appears very
different to the others but, seen through the lens of this paper, it is very
close indeed.}, each by the composition of the two design choices
(\S\ref{sec-implementations}). Doing this modelling in a single setting
allows the differences and similarities between these huge systems to be
brought out clearly\footnote{All our models are executable and are available on
Hackage: \url{https://hackage.haskell.org/package/build-0.0.1.1}.}.

>>>>

\item We show that we can instantiate our abstractions to describe the essence
of a variety of different real-life build systems, including \Make, \Shake,
\Bazel, \CloudBuild, \Buck, \Nix, and \Excel\footnote{\Excel appears very
different to the others but, seen through the lens of this paper, it is very
close indeed.}, each by the composition of the two design choices
(\S\ref{sec-implementations}). Doing this modelling in a single setting
allows the differences and similarities between these huge systems to be
brought out clearly\footnote{All our models are executable and are available on
Hackage: \url{https://hackage.haskell.org/package/build-1.0}.}.
